%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV Cover Letter Template
%
% This template uses the same styling as resume.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Override color
\colorlet{awesome}{awesome-darknight}

%%% Configure a separator for social information in header
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\name{Ada Noelle}{Young}
\address{3412 Garden Dr. Knoxville TN, 37918}
\mobile{(+1) 865.384.1256}
\email{adanoelleyoung@gmail.com}
\github{adanoelle}
\position{legal name: M. Todd Young}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Hiring Manager}
  {Advanced Computing in Health Sciences\\Oak Ridge National Laboratory\\Oak Ridge, TN 37830}
\letterdate{\today}
\lettertitle{Application for Machine Learning Data Engineer}
\letteropening{Dear Hiring Manager,}
\letterclosing{Sincerely,}
%\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

% Print the header
\makecvheader

% Print the letter title
\makelettertitle

\begin{cvletter}

I am writing to express my interest in the Machine Learning Data Engineer position
within the Advanced Computing in Health Sciences section at Oak Ridge National
Laboratory. Having spent four years at ORNL developing machine learning methods for
healthcare research, I am excited about the opportunity to return and contribute to
the intersection of high-performance computing and biomedical research.

During my time at ORNL (2017-2021), I developed deep learning pipelines for
HIPAA-compliant clinical data, built production infrastructure for the CANDLE project
spanning multiple national laboratories, and published research in venues including
JAMIA and IEEE Journal of Biomedical and Health Informatics. I worked on the Titan
and Summit supercomputers, as well as DGX systems, implementing distributed training
workflows using PyTorch, Horovod, DeepSpeed, and PyTorch Distributed.

My subsequent role at Pinnacle Reliability broadened my perspective on production
machine learning systems. I led the transformation of a 60,000-line monolithic
codebase into a scalable microservices architecture and served as the technical
bridge between research mathematicians and software engineers. I learned to design
abstractions that let researchers focus on domain problems while ensuring
production-quality implementations, skills I want to bring back to a research
environment.

I had originally planned to pursue a PhD while at ORNL, a path I was exploring with
potential advisors at the lab before extenuating circumstances made this difficult.
My hope is that this position would open the possibility of re-engaging that goal
while contributing to impactful healthcare informatics projects. This role would let
me bring together my research background, machine learning expertise, and production
infrastructure experience in service of ACH's mission. I have institutional knowledge
of the NCI pathology dataset, familiarity with ORNL's computing resources, and a track
record of cross-team collaboration, working with researchers across the labs and
industry.

The opportunity to return to a research environment where advancing scientific
knowledge is the primary mission is compelling. My industry experience strengthened
my software engineering and infrastructure capabilities, skills that I believe will
strengthen your research team's work. I would welcome the opportunity to discuss how
my combination of ORNL research experience and production ML infrastructure expertise
can support your team's goals. Thank you for your consideration.

\end{cvletter}

% Print the closing
\vspace{3.4mm}
Sincerely,\\[4mm]
\textbf{Ada Young}

\end{document}
